### 2024-09-08 draft-2/draft-2.tex
move dfz range from definition of position to definition of valid position

\minor Message terminators divide the client and engine streams into
\term{messages}; that is, a message is a (possibly empty) subsequence of bytes
that does not contain a message terminator and every byte of the client and
engine streams is either part of a message or part of a message terminator.
The messages within the client stream are \term{client messages} and the
messages within the engine stream are \term{engine messages}.
\vskip-\parskip
\greybox{This precludes the proper use of some encodings, such as
{\caps utf-16} (since in {\caps utf-16}, the byte \hex{0a} appears in the
encodings of various scalar values, whereas in {\caps utf-8}, the byte
\hex{0a} only appears in the encoding for \uni{000a line feed}).}

@@

@@

\vskip-0.5\parskip A nonnegative integer called the \term{depth from zeroing},
which is 100 or less. \comment{This is the number of moves that have been played
(none of which are captures or pawn moves) since the last capture or pawn move,
measured in ply.}

@@

>>>>

\minor Message terminators divide the client and engine streams into
\term{messages}; that is, a message is a (possibly empty) subsequence of bytes
that does not contain a message terminator and every byte of the client and
engine streams is either part of a message or part of a message terminator.
The messages within the client stream are \term{client messages} and the
messages within the engine stream are \term{engine messages}.
\vskip-\parskip
\greybox{This precludes the proper use of some encodings, such as {\caps utf-16}
or {\caps utf-32} (since in {\caps utf-16} and {\caps utf-32}, the byte \hex{0a}
appears in the encodings of various scalar values, whereas in {\caps utf-8}, the
byte \hex{0a} only appears in the encoding for \uni{000a line feed}).}

@@

% TODO when the remainder of a message is viewed as bytes, are both leading
%   and trailing spaces stripped?

@@

\vskip-0.5\parskip A nonnegative integer called the \term{depth from zeroing}.
\comment{This is the number of moves that have been played (none of which are
captures or pawn moves) since the last capture or pawn move, measured in ply.}

@@

\vskip-0.5\parskip The depth from zeroing is 100 or less.
